---
title: "PBMC main type"
author: "`r config::get(file = 'Config.yml')$document$author`"
date: "`r Sys.Date()`"
output:
  pdf_document:
    keep_tex: true
    latex_engine: pdflatex
    fig_caption: yes
    highlight: haddock
    number_sections: yes
knit: (
  function(inputFile, encoding) {
    Config=config::get(file = 'Config.yml') 
    
    pSubTitle <- paste0("PBMC_maintype",".pdf")
    
    base_output_dir <- Config$base_output_dir
 
    rmarkdown::render( 
      input       = inputFile, 
      encoding    = encoding, 
      output_file = pSubTitle,
      output_dir = base_output_dir )}
    )

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,include=F,warning=F)
```



```{r,include=F}
rm(list=ls())
#install.packages('Seurat')
#BiocManager::install("scran")
# BiocManager::install("S4Vectors")
# BiocManager::install("cytolib")
# BiocManager::install("scuttle")
#BiocManager::install("scMerge")


# install.packages('ggrastr')
#BiocManager::install("scater")
#remotes::install_version("Matrix", version = "1.6-1")
library("scater")
#BiocManager::install("SingleR")
library(dplyr)
library(ggplot2)
library(scran)
library(scuttle)
library(bluster)
library(SingleR)
#library("Seurat")

```


```{r,include=T}
Config=config::get(file = 'Config.yml')
Path=Config$Path
Rawdata_path=file.path(Path, "R/Rawdata")
Rcode_path=file.path(Path, "R/Rcode")
```



```{r,include=F}
# Sample annotation
SRA_sample=read.csv(file.path(Rawdata_path,"SraRunInfo.csv" ))
SRA_sample_anno=SRA_sample[,c("LibraryName","Run")]%>%mutate(Group=c(rep("Gout_SYN",3),rep("Gout_PBMC",7),rep("Control_PBMC",5)))%>%setNames(c("Sample_ID","SRR_number","Group"))
scdata_Samples_ID2=SRA_sample[,c("LibraryName","Run")]%>%mutate(Group=c(rep("Gout_SYN",3),rep("Gout_PBMC",7),rep("Control_PBMC",5)))%>%setNames(c("Sample_ID","SRR_number","Group"))%>%mutate(Sample_ID2=c(paste0("Gout_SYN_",c(1:3)),paste0("Gout_PBMC_",c(1:7)),paste0("Control_PBMC_",c(1:5)) ))
```


```{r,include=T}
knitr::kable(scdata_Samples_ID2,caption = "Sample information")
```

# Set up Gout subgroup by drinking habit (# Te clinical conditions of seven patients with acute gout are shown in Table S1. Among these patients, only Case 07 was a new case, with the frst attack lasting for 19 days; all others had a disease history of 1 to>20 years, with attacks lasting 1–14 days. Cases 03 and 07 were heavy drinkers, and Case 05 drink occasionally; the other subjects did not drink.


```{r,eval=T}
# Merge scData
       
if (! file.exists(file.path(Rawdata_path,"PBMC_subtype_update.rdata"))){
 load(file.path(Rawdata_path,"Clean_scRNA_and_metadata.rdata"))

 PBMC_Data=scData_label[4:15]
 PBMC_sce_combine=scMerge::sce_cbind(PBMC_Data,colData_names =T,batch_names =scdata_Samples_ID2$Sample_ID2[4:15] )
 set.seed(12345)
 PBMC_sce_combine2<-  scater::runPCA(PBMC_sce_combine, name="PCA2",ncomponents=50)
 set.seed(12345)
 PBMC_sce_combine2 <-  scater::runTSNE(PBMC_sce_combine2, perplexity=20, 
    dimred="PCA2", n_dimred=10)
 PBMC_sce_combine2$batch=factor(PBMC_sce_combine2$batch,levels = unique(PBMC_sce_combine2$batch))


 save(PBMC_sce_combine2,scdata_Samples_ID2,file=file.path(Rawdata_path,"PBMC_subtype_update.rdata"))
} else{
  
  load(file.path(Rawdata_path,"PBMC_subtype_update.rdata"))
}

```


```{r,eval=T}
PBMC_Samples_ID3= scdata_Samples_ID2%>%mutate(Group2=ifelse(Sample_ID2%in%c("Gout_PMBC_3","Gout_PBMC_5","Gout_PBMC_7"),"Gout_PBMC_type1",ifelse(grepl("Gout_PBMC",Sample_ID2),"Gout_PBMC_type2",Group   ) ))%>%dplyr::filter(grepl("PBMC",Group))
                                                              
PBMC_Samples_ID3$Group2=factor(PBMC_Samples_ID3$Group2,levels=c("Control_PBMC","Gout_PBMC_type1","Gout_PBMC_type2"))
Main_celltype=c("B_cell","CD4+_T_cell","CD8+_T_cell","T_cell","NK_cell","Monocyte","Neutrophils","Macrophage","DC" ,"Platelets")
All_celltype_color=c(RColorBrewer::brewer.pal(n = 9, name = "Set1") ,RColorBrewer::brewer.pal(n = 2, name = "Set2"))
names(All_celltype_color)=c(Main_celltype,"Other") 

Coldata=colData(PBMC_sce_combine2)
```

```{r,eval=T}
head(reducedDim(PBMC_sce_combine2 , "TSNE"))
newcolor=All_celltype_color[unique(PBMC_sce_combine2$labels)]

```

# TSNE PLOT 

```{r,fig.height=16,fig.width=12,warning=F,eval=T}
Control_sce=PBMC_sce_combine2%>%subset(.,,grepl("Control",batch))
Gout_type1=PBMC_sce_combine2%>%subset(.,,batch%in%c("Gout_PBMC_3","Gout_PBMC_7"))
Gout_type2=PBMC_sce_combine2%>%subset(.,,batch%in%c("Gout_PBMC_1","Gout_PBMC_2","Gout_PBMC_4","Gout_PBMC_5","Gout_PBMC_6"))
```
 

```{r,fig.height=8,fig.width=12,warning=F,include=F}
P1=scater::plotTSNE(Control_sce, colour_by="labels")+scale_color_manual(values =All_celltype_color )+facet_wrap(colData(Control_sce)$batch,nrow=1)+theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 1), 
        strip.background = element_rect(color = "black", size = 1))

P2=scater::plotTSNE(Gout_type1, colour_by="labels")+scale_color_manual(values =All_celltype_color )+facet_wrap(colData(Gout_type1)$batch,nrow=1)+theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 1), 
        strip.background = element_rect(color = "black", size = 1))

P3=scater::plotTSNE(Gout_type2, colour_by="labels")+scale_color_manual(values =All_celltype_color )+facet_wrap(colData(Gout_type2)$batch,nrow=1)+theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 1), 
        strip.background = element_rect(color = "black", size = 1))
  
```



 
```{r,fig.height=16,fig.width=12,warning=F,include=T}
cowplot::plot_grid(plotlist=list(P1,P2,P3),nrow=3,scale=c(1,0.5,0.8))
```



```{r,fig.width=12,fig.height=10}
Plotlist=list()
Datalist=list(Control_sce,Gout_type1,Gout_type2 )
Names=c("Control","Gout_PBMC_type1","Gout_PBMC_type2")
for ( i in 1:3 ) {
 name=Names[i]
 Data=Datalist[[i]]
 Cell_type_sum=data.frame(Celltype=Data$labels,Sample=colData(Data)$batch) 
 Cell_type_sum2=Cell_type_sum%>% group_by(Sample,Celltype)%>%summarise(n=n())
 Cell_type_sum_n2= Cell_type_sum2%>%group_by(Sample)%>%summarise(total=sum(n))
 Cell_type_sum3=Cell_type_sum2%>%left_join(.,Cell_type_sum_n2)%>%mutate(Per=scales::percent( n/total))
 Plotlist[[name]]=ggplot(Cell_type_sum2, aes(x="",y=n, fill=Celltype))+
  geom_bar(width = 1,stat = "identity",position="fill")+scale_color_manual(values =newcolor )+
  coord_polar("y",start=0)+facet_wrap(~Sample,nrow=1)

}

```

# main Cell types in each samples (The lack of low-density neutrophils in the blood may have resulted from the experimental procedure used for mononuclear cell selection)

```{r,fig.width=15,fig.height=12,include=T}
cowplot::plot_grid(plotlist = Plotlist,ncol = 1)
```

```{r}
Data=PBMC_sce_combine2
Cell_type_sum=data.frame(Celltype=Data$labels,Sample=colData(Data)$batch) %>%mutate(Maintype=ifelse(Celltype%in%c("B_cell","T_cell","CD4+_T_cell","CD8+_T_cell","NK_cell"),"Lymphocyte",ifelse(Celltype%in%c("Monocyte","Neurophils","DC"),"Myeloid" ,"Other")))

Cell_type_sum2=Cell_type_sum%>% group_by(Sample,Maintype)%>%summarise(n=n())
Cell_type_sum_n2= Cell_type_sum2%>%group_by(Sample)%>%summarise(total=sum(n))
Cell_type_sum3=Cell_type_sum2%>%left_join(.,Cell_type_sum_n2)%>%mutate(Per=scales::percent( n/total),proportion=n/total)%>%mutate(Group2=ifelse(Sample%in%c("Gout_PMBC_3","Gout_PBMC_5","Gout_PBMC_7"),"Gout_PBMC_type1",ifelse(grepl("Gout_PBMC",Sample),"Gout_PBMC_type2","Control_PBMC"  ) ))%>%mutate(Group=ifelse(grepl("Control",Sample),"Control_PBMC","Gout_PBMC"))

```


# Lymphocyte and Myeloid
```{r,fig.width=10,fig.height=12,include=T}
library(ggrepel)
Cell_type_sum3_select=Cell_type_sum3%>%dplyr::filter(Maintype!="Other")

P1=ggplot(Cell_type_sum3_select,aes(x=Group,y=proportion,fill=Group))+geom_boxplot()+geom_point() + ggpubr:: stat_compare_means()+ facet_wrap(~Maintype,ncol=2)

P2=ggplot(Cell_type_sum3_select,aes(x=Group2,y=proportion,fill=Group))+geom_boxplot()+geom_point() + ggpubr:: stat_compare_means()+ facet_wrap(~Maintype,ncol=2)

cowplot::plot_grid(P1,P2,nrow=2)

```

# Subtypes

```{r}
# Statistic analysis
Data=PBMC_sce_combine2
Cell_type_sum=data.frame(Celltype=Data$labels,Sample=colData(Data)$batch) 

Cell_type_sum2=Cell_type_sum%>% group_by(Sample,Celltype)%>%summarise(n=n())
Cell_type_sum_n2= Cell_type_sum2%>%group_by(Sample)%>%summarise(total=sum(n))
Cell_type_sum3=Cell_type_sum2%>%left_join(.,Cell_type_sum_n2)%>%mutate(Per=scales::percent( n/total),proportion=n/total)%>%mutate(Group2=ifelse(Sample%in%c("Gout_PMBC_3","Gout_PBMC_5","Gout_PBMC_7"),"Gout_PBMC_type1",ifelse(grepl("Gout_PBMC",Sample),"Gout_PBMC_type2","Control_PBMC"  ) ))%>%mutate(Group=ifelse(grepl("Control",Sample),"Control_PBMC","Gout_PBMC"))
Cell_type_sum3%>%dplyr::filter(Celltype=="Monocyte")
```


```{r,fig.width=12,fig.height=16,include=T}
library(ggrepel)
ggplot(Cell_type_sum3,aes(x=Group,y=proportion,fill=Group))+geom_boxplot()+geom_point() + ggpubr:: stat_compare_means()+ facet_wrap(~Celltype,nrow=3)



```

```{r,fig.width=12,fig.height=16}
library(ggrepel)
ggplot(Cell_type_sum3,aes(x=Group2,y=proportion,fill=Group))+geom_boxplot()+geom_point() + ggpubr:: stat_compare_means()+ facet_wrap(~Celltype,nrow=3)



```

```{r}
knitr::knit_exit()
```

