---
title: "SF immune"
author: "`r config::get(file = 'Config.yml')$document$author`"
date: "`r Sys.Date()`"
output:
  pdf_document:
    keep_tex: true
    latex_engine: pdflatex
    fig_caption: yes
    highlight: haddock
    number_sections: yes
knit: (
  function(inputFile, encoding) {
    Config=config::get(file = 'Config.yml') 
    
    pSubTitle <- paste0("SF immune",".pdf")
    
    base_output_dir <- Config$base_output_dir
 
    rmarkdown::render( 
      input       = inputFile, 
      encoding    = encoding, 
      output_file = pSubTitle,
      output_dir = base_output_dir )}
    )

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,include=F,warning=F)
```



```{r,include=F}
rm(list=ls())
#install.packages('Seurat')
#BiocManager::install("scran")
# BiocManager::install("S4Vectors")
# BiocManager::install("cytolib")
# BiocManager::install("scuttle")
#BiocManager::install("scMerge")


# install.packages('ggrastr')
#BiocManager::install("scater")
#remotes::install_version("Matrix", version = "1.6-1")
library("scater")
#BiocManager::install("SingleR")
library(dplyr)
library(ggplot2)
library(scran)
library(scuttle)
library(bluster)
library(SingleR)
#library("Seurat")

```


```{r,include=T}
Config=config::get(file = 'Config.yml')
Path=Config$Path
Rawdata_path=file.path(Path, "R/Rawdata")
Rcode_path=file.path(Path, "R/Rcode")
```



```{r,include=F}
# Sample annotation
SRA_sample=read.csv(file.path(Rawdata_path,"SraRunInfo.csv" ))
SRA_sample_anno=SRA_sample[,c("LibraryName","Run")]%>%mutate(Group=c(rep("Gout_SYN",3),rep("Gout_PBMC",7),rep("Control_PBMC",5)))%>%setNames(c("Sample_ID","SRR_number","Group"))
scdata_Samples_ID2=SRA_sample[,c("LibraryName","Run")]%>%mutate(Group=c(rep("Gout_SYN",3),rep("Gout_PBMC",7),rep("Control_PBMC",5)))%>%setNames(c("Sample_ID","SRR_number","Group"))%>%mutate(Sample_ID2=c(paste0("Gout_SYN_",c(1:3)),paste0("Gout_PBMC_",c(1:7)),paste0("Control_PBMC_",c(1:5)) ))
```


```{r,include=T}
knitr::kable(scdata_Samples_ID2,caption = "Sample information")
```

# Set up Gout subgroup by drinking habit (# Te clinical conditions of seven patients with acute gout are shown in Table S1. Among these patients, only Case 07 was a new case, with the frst attack lasting for 19 days; all others had a disease history of 1 to>20 years, with attacks lasting 1–14 days. Cases 03 and 07 were heavy drinkers, and Case 05 drink occasionally; the other subjects did not drink.


```{r,eval=T}
# Merge scData
       
if (! file.exists(file.path(Rawdata_path,"Three_synoval_immune.rdata"))){
 load(file.path(Rawdata_path,"Clean_scRNA_and_metadata.rdata"))
 SF_data_sce=scData_label[1:3]
 sce_combine=scMerge::sce_cbind(SF_data_sce,colData_names =T,batch_names =scdata_Samples_ID2$Sample_ID2[1:3] )
 #sce_combine$labels
 set.seed(1234)
 sce_combine2<-  scater::runPCA(sce_combine, name="PCA2",ncomponents=50)
 sce_combine2 <-  scater::runTSNE(sce_combine2, perplexity=20, 
    dimred="PCA2", n_dimred=10)
 sce_combine2$batch=factor(sce_combine2$batch,levels = c("Gout_SYN_1","Gout_SYN_2","Gout_SYN_3"))
 clust.kmeans <- scran::clusterCells(sce_combine2, use.dimred="PCA2", BLUSPARAM= bluster::KmeansParam(centers=5))
 sce_combine2$Kmeans=clust.kmeans
unique(sce_combine2$labels)
table(sce_combine2$labels)
 sce_combine2= scater::runUMAP (sce_combine2, name="UMAP", dimred="PCA2",  n_neighbors = 10)
P1=scater::plotUMAP(sce_combine2, colour_by="Kmeans",,text_by="Kmeans") 
P2=scater::plotUMAP(sce_combine2, colour_by="labels",,text_by="labels")

Classical_kmeans=data.frame(Cluster=sce_combine2$Kmeans,Subtype=sce_combine2$labels)%>%mutate(Subtype=gsub("Monocyte","Macrophage",Subtype))%>%mutate(Subtype=ifelse(Subtype=="Macrophage"&Cluster%in%c(4,5),"M2_macro", ifelse(Subtype=="Macrophage","M1_macro",Subtype )))
table(Classical_kmeans$Subtype)
sce_combine2$Subtype=Classical_kmeans$Subtype
SF_data_sce=sce_combine2
save(SF_data_sce,file=file.path(Rawdata_path,"Three_synoval_immune.rdata"))
} else{
  
  load(file.path(Rawdata_path,"Three_synoval_immune.rdata"))
}
# Myeloid data from SF 
```

# Main subtypes (SingleR and  singleR+kmeans)
```{r,fig.height=18,fig.width=12,include=T}
P1=scater::plotUMAP(SF_data_sce, colour_by="labels",,text_by="labels") 
P2=scater::plotUMAP(SF_data_sce, colour_by="Subtype",,text_by="Subtype")
 
cowplot::plot_grid(P1,P2,ncol=2) 
 
```


```{r,eval=T}
#load(file.path(Rawdata_path,"Three_synoval_immune.rdata")) # immune cells in synovial 

Main_celltype=c("B_cell","CD4+_T_cell","CD8+_T_cell","NK_cell","Monocyte","Neutrophils","Macrophage","DC" ,"Platelets", "M1_macro","M2_macro")
All_celltype_color=c(RColorBrewer::brewer.pal(n = 9, name = "Set1") ,RColorBrewer::brewer.pal(n = 4, name = "Set2"))
names(All_celltype_color)=c(Main_celltype,"Other")
```



# M2 markers ,"CD68","MRC1/CD206","cd163; M1 marker: CD68+;State markers: CD14, CD86,"ITGAM","CD14","FCGR3A" ,,"CD86"

```{r,fig.height=8,fig.width=12,include=T}
# M1 and M2 marker https://www.origene.com/research-areas/m1-and-m2-macrophage-markers
# CD16a:FCGR3A;cd11c:ITGAX,CD20:MS4A1;CD19:MANE.CD11B:ITGAM,CD206: MRC1
# Flt3+ macrophage precursors
# Neutrophils: IFITM2, IFITM1, H3F3B, SAT1, and S100A8 
# CD16b"FCGR3B" missing in the data
markers=c("CD68","MRC1","CD163","ITGAM","CD14","FCGR3A" ,"CD86","FLT3")

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}

rownames(SF_data_sce)%>%.[grepl("FCGR",.)]

cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

# T cells  markers (MostT cells are NKT cells)
```{r,fig.height=18,fig.width=12,include=T}
# M1 and M2 marker https://www.origene.com/research-areas/m1-and-m2-macrophage-markers
# CD16a:FCGR3A;cd11c:ITGAX,CD20:MS4A1;CD19:MANE.CD11B:ITGAM,CD206: MRC1
# Flt3+ macrophage precursors
# Neutrophils: IFITM2, IFITM1, H3F3B, SAT1, and S100A8 
# CD16b"FCGR3B" missing in the data
markers=c("CD3E" , "CD3D","CD3G" ,"CD4","CD8A","CD8B","GZMB","GNLY","NKG7","ITGAM","CD14","FCGR3A" ,"CD68","MRC1","CD86","IL1R2","IL1R1","HLA-DQB1","HLA-DQA1" , "FLT3" ,"ITGAX","CXCL2","IFITM2", "IFITM1", "H3F3B")

markers=c("CD3E" , "CD3D","CD3G" ,"CD4","CD8A","CD8B","GZMB","GNLY","NKG7")
Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}

rownames(SF_data_sce)%>%.[grepl("FCGR",.)]

cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

```{r,include=T}
newcolor=All_celltype_color[unique(SF_data_sce$Subtype)]

scater::plotUMAP(SF_data_sce, colour_by="Subtype")+facet_wrap(SF_data_sce$batch)+theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 1), 
        strip.background = element_rect(color = "black", size = 1))

```

```{r,fig.width=12,fig.height=4,include=T}
Classical_kmeans2=data.frame(Cluster=SF_data_sce$Subtype,Sample=SF_data_sce$batch) 
Classical_kmeans_data2=Classical_kmeans2%>% group_by(Sample,Cluster)%>%summarise(n=n())
Classical_kmeans_data_n2= Classical_kmeans_data2%>%group_by(Sample)%>%summarise(total=sum(n))
Classical_kmeans_data3=Classical_kmeans_data2%>%left_join(.,Classical_kmeans_data_n2)%>%mutate(Per=scales::percent( n/total))


ggplot(Classical_kmeans_data3, aes(x="",y=n, fill=Cluster))+
  geom_bar(width = 1,stat = "identity",position="fill")+
  coord_polar("y",start=0)+facet_wrap(Classical_kmeans_data3$Sample)

```

# M2 showed high expression of IL1B
```{r,fig.height=12,fig.width=12,include=T}
markers=rownames(SF_data_sce)%>%.[grepl("^IL",.)]%>%.[!grepl("R|P|BL|DT|K|ST",.)]
Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}


cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```


# Chemokines
```{r,fig.height=12,fig.width=12,include=T}
markers=rownames(SF_data_sce)%>%.[grepl("^CXC",.)]

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}


cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

# CSF
```{r,fig.height=12,fig.width=12,include=T}
markers=rownames(SF_data_sce)%>%.[grepl("^CSF",.)]

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}


cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```
\newpage

# NFKB,RELA(NFKB3)
```{r,fig.height=12,fig.width=12,include=T}
markers=rownames(SF_data_sce)%>%.[grepl("NFKB|RELA",.)]

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}


cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

```{r}
Gene_expression_celltype=function(SCE,genename) {
  library("SingleCellExperiment")
  p1 <- colData(SCE) %>%as.data.frame()%>%
  mutate(expression =logcounts(SCE) [genename,]) %>%
  ggplot(aes(x = Subtype, y = expression, fill = Subtype)) +
  geom_violin(draw_quantiles = c(0.5), scale = 'width', trim = TRUE) +
  theme_bw() +
  #scale_fill_manual(values = custom_colors$discrete) +
  scale_x_discrete() +
  scale_y_continuous(name = 'Log-normalized expression', labels = scales::comma) +
  labs(title =paste0(genename  ,"_expression")) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    legend.position = 'none'
  )
  
}


```

\newpage
```{r,fig.height=4,fig.width=12,include=T}
Gene_list=c("IL1B", "NFKB1","CD68", "CD163","HLA-DQA1","HLA-DQB1" ) 

Plotlist=list()
for (i in Gene_list) {
  Plotlist[[i]]=Gene_expression_celltype(SF_data_sce,i) 

}

cowplot::plot_grid(plotlist= Plotlist,ncol=3)

```

# PIEZO,KCNN,NGF

```{r,fig.height=12,fig.width=12,include=T}

markers=rownames(SF_data_sce)%>%.[grepl("PIEZO|KCNN|NGF|TGFB",.)]

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}


cowplot::plot_grid( plotlist=Fig_list,ncol=4)

```
\newpage

```{r,fig.height=10,fig.width=12,include=T}
Gene_list=rownames(SF_data_sce)%>%.[grepl("PIEZO|KCNN|NGF|TGFB",.)]


Plotlist=list()
for (i in Gene_list) {
  Plotlist[[i]]=Gene_expression_celltype(SF_data_sce,i) 

}

cowplot::plot_grid(plotlist= Plotlist,ncol=3)

```


```{r}
knitr::knit_exit()
```


# Differential expressed genes between cell types

```{r}
sce=SF_data_sce
dea <- scran::pseudoBulkDGE(sce, label =NULL, condition = sce$Subtype, design =~0+ condition, contrast = c("M1_macro", "M2_macro"))
```



```{r}
knitr::knit_exit()
```


```{r}
sce=SF_data_sce
library(scater)
sce_counts <-counts(sce)
colData(sce)$pb_group =
    paste0(colData(sce)$batch,
           "-",
           colData(sce)$Subtype)

sce_counts <- counts(sce)
pb_counts <- t(rowsum(t(sce_counts), colData(sce)$pb_group))

pb_samples <- colnames(pb_counts)
#pb_samples <- gsub("astrocytes_ependymal", "astrocytes-ependymal", pb_samples)
pb_split <- do.call(rbind, strsplit(pb_samples, "-"))
pb_sample_anno <- data.frame(
    sample = pb_samples,
    cell_type = pb_split[, 2],
    sample_group = pb_split[, 1]
)

pb_dge <- edgeR:: DGEList(
    counts = pb_counts,
    samples = pb_sample_anno,
    group = pb_sample_anno$cell_type
)

pb_dge <- edgeR::calcNormFactors(pb_dge)

#design <- model.matrix(~sample_group + cell_type, data = pb_dge$samples)
design <- model.matrix(~0 + cell_type, data = pb_dge$samples)

colnames(design) <- make.names(gsub("cell_type", "", colnames(design)))
colnames(design) <- make.names(gsub("sample_group", "", colnames(design)))

pb_dge <-  edgeR::estimateDisp(pb_dge, design)
```


```{r}
library(edgeR)
contr <- makeContrasts("M1_macro - M2_macro", levels = design)

pb_fit <- glmFit(pb_dge, design)
pb_lrt <- glmLRT(pb_fit, contrast = contr)
```

```{r}
#BiocManager::install("Glimma")
Glimma::glimmaMA(pb_lrt, dge = pb_dge)
```


```{r}
Gene_expression=function(sce_Data,gene_name){
  Expression=sce_Data
  Data=data.frame(Subtype=sce_Data$Subtype,Batch=SF_data_sce$batch) 

  
}
```


```{r}
knitr::knit_exit()
```


```{r,include=F}
SF_data_sce.markers =scran::scoreMarkers(SF_data_sce,groups=SF_data_sce$Subtype)
names(SF_data_sce.markers)

Type1_marker=SF_data_sce.markers[["Other"]]%>%as.data.frame()%>%dplyr::filter( mean.AUC>0.7) %>%arrange   (desc(mean.logFC.cohen))
Type2_marker=SF_data_sce.markers[["NK_cells"]]%>%as.data.frame()%>%dplyr::filter( mean.AUC>0.7) %>%arrange   (desc(mean.logFC.cohen))
Type3_marker=SF_data_sce.markers[["T_cells"]]%>%as.data.frame()%>%dplyr::filter( mean.AUC>0.7) %>%arrange   (desc(mean.logFC.cohen))

```





```{r,fig.height=18,fig.width=12}
# M1 and M2 marker https://www.origene.com/research-areas/m1-and-m2-macrophage-markers
# CD16a:FCGR3A;cd11c:ITGAX,CD20:MS4A1;CD19:MANE.CD11B:ITGAM,CD206: MRC1
# Flt3+ macrophage precursors
# Neutrophils: IFITM2, IFITM1, H3F3B, SAT1, and S100A8 
# CD16b"FCGR3B" missing in the data
markers=c("CD3E" , "CD3D","CD3G" ,"CD4","CD8A","CD8B","GZMB","GNLY","NKG7","ITGAM","CD14","FCGR3A" ,"CD68","MRC1","CD86","IL1R2","IL1R1","HLA-DQB1","HLA-DQA1" , "FLT3" ,"ITGAX","CXCL2","IFITM2", "IFITM1", "H3F3B")

markers=c("CD3E" , "CD3D","CD3G" ,"CD4","CD8A","CD8B","GZMB","GNLY","NKG7")
Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}

rownames(SF_data_sce)%>%.[grepl("FCGR",.)]

cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```


```{r,fig.height=8,fig.width=12}
# M1 and M2 marker https://www.origene.com/research-areas/m1-and-m2-macrophage-markers
# CD16a:FCGR3A;cd11c:ITGAX,CD20:MS4A1;CD19:MANE.CD11B:ITGAM,CD206: MRC1
# Flt3+ macrophage precursors
# Neutrophils: IFITM2, IFITM1, H3F3B, SAT1, and S100A8 
# CD16b"FCGR3B" missing in the data
markers=c("ITGAM","CD14","FCGR3A" ,"CD68","MRC1","CD86")

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}

rownames(SF_data_sce)%>%.[grepl("FCGR",.)]

cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

```{r,fig.height=18,fig.width=12}
markers=rownames(SF_data_sce)%>%.[grepl("^IL",.)]%>%.[!grepl("R|P|BL|DT|K|ST",.)]%>%sort()

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}

rownames(SF_data_sce)%>%.[grepl("^IL",.)]%>%.[!grepl("R|P|BL|DT|K|ST",.)]

cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

```{r,fig.height=12,fig.width=12}
markers=rownames(SF_data_sce)%>%.[grepl("^CXC",.)]

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}

rownames(SF_data_sce)%>%.[grepl("^IL",.)]%>%.[!grepl("R|P|BL|DT|K|ST",.)]

cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

```{r,fig.height=12,fig.width=12}
markers=rownames(SF_data_sce)%>%.[grepl("^CCL",.)]

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}

rownames(SF_data_sce)%>%.[grepl("^IL",.)]%>%.[!grepl("R|P|BL|DT|K|ST",.)]

cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

```{r,fig.height=6,fig.width=12}
markers=rownames(SF_data_sce)%>%.[grepl("CSF",.)]

Fig_list=list()
for (i in markers){
  Fig_list[[i]]=scater::plotUMAP (SF_data_sce, colour_by=i)+ ggtitle(label = i) + theme(plot.title = element_text(size = 20))
  
}

rownames(SF_data_sce)%>%.[grepl("^IL",.)]%>%.[!grepl("R|P|BL|DT|K|ST",.)]

cowplot::plot_grid( plotlist=Fig_list,ncol=4)
```

```{r}
newcolor=All_celltype_color[unique(SF_data_sce$labels)]

scater::plotUMAP(SF_data_sce, colour_by="Subtype")+facet_wrap(SF_data_sce$batch)+theme(panel.spacing = unit(.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 1), 
        strip.background = element_rect(color = "black", size = 1))

```




```{r}
Mye_types=c("Monocyte","Neutrophils","Macrophage","DC")

SF_data_Myeloid=lapply(SF_data,function(x) x[,x$labels%in%Mye_types] )

unique(SF_data_Myeloid[[1]]$labels)

```


```{r}
hpca.ont <- celldex::HumanPrimaryCellAtlasData(ensembl=F, cell.ont="nonna")
bpe.ont <- celldex::BlueprintEncodeData(ensembl=F, cell.ont="nonna")

# Using the same sets of genes:
shared <- intersect(rownames(hpca.ont), rownames(bpe.ont))
hpca.ont_shared <- hpca.ont[shared,]
bpe.ont_shared <- bpe.ont[shared,]

 
```

```{r}
Mye_pred=list()
Select_Data=SF_data_Myeloid
 
for (i in 1:length(Select_Data)){
  scdata=Select_Data[[i]]
  Pred2= SingleR::SingleR(test =scdata, assay.type.test=1,  ref = list( HPCA=hpca.ont_shared,BPE=bpe.ont_shared ), 
    labels = list(hpca.ont_shared$label.main,bpe.ont_shared$label.main))
  
  All_celltype=Pred2$pruned.labels%>%gsub("Monocytes","Monocyte" ,. )%>%gsub("Macrophages","Macrophage" ,. )%>%gsub("cells","cell" ,. )
  #Pred= SingleR::SingleR(test =scdata, assay.type.test=1,  ref = hpca.ont,labels=hpca.ont $label.main)
  #All_celltype_anno=data.frame(labels=All_celltype)%>%mutate(label2=ifelse(labels%in%Main_celltype,labels,"Other"))
  #Pred$labels=All_celltype
  Mye_pred[[i]]=All_celltype 
 
  
}


```

```{r,eval=T}
# All_celltype_color=RColorBrewer::brewer.pal(n = 4, name = "Set1") 
# names(All_celltype_color)=c(Mye_types) 

Main_celltype=c("B_cell","T_cells","NK_cell","Monocyte","Neutrophils","Macrophage","DC" ,"Platelets")

All_celltype_color=RColorBrewer::brewer.pal(n = 9, name = "Set1") 
names(All_celltype_color)=c(Main_celltype,"Other") 
```
 

```{r,eval=T,fig.height=16,fig.width=12}
Cell_anno=Mye_pred
Data=SF_data_Myeloid
figure_list=list()
newcolor=All_celltype_color[Mye_types]
# 
# #Predict_data=Mye_pred
# for (i in 1:length(sc_data)){
#  set.seed(1234)
#  sce=sc_data[[i]]
#  #data=Clean_scdata[[i]]
#  #sce <- logNormCounts(Seurat::as.SingleCellExperiment(data))
#  dec <- modelGeneVarByPoisson(sce)
#  sce2 <- denoisePCA(sce, dec, subset.row=getTopHVGs(dec, n=5000))
#  colLabels(sce2) <- clusterRows(reducedDim(sce2), NNGraphParam())
#  set.seed(117)
#  scelist[[i]]<-scater::runTSNE(sce2, dimred="PCA")
#  scelist[[i]]$labels=Mye_anno[[i]]$pruned.labels
# #
# 
# }


for(i in 1:length(Data)){
 set.seed(1234)
 sce=Data[[i]]
 sce$labels=Cell_anno[[i]]
 #sce$labels=gsub(NA,"Other",sce$labels)
 dec <- modelGeneVarByPoisson(sce)
 sce2 <- denoisePCA(sce, dec, subset.row=getTopHVGs(dec, n=5000))
 nn <- RANN::nn2(reducedDim(sce2, "PCA"), k = 50)
 names(nn) <- c("idx", "dist")
 g <- buildKNNGraph(sce2, k = 30, use.dimred = "PCA")
 reducedDim(sce2, "KNN") <- igraph::as_adjacency_matrix(g)


# Run UMAP and rename it for comparisson temp <- umap::umap.defaults
 try(reducedDim(sce2, "UMAP_on_Graph") <- NULL)
 reducedDim(sce2, "UMAP_on_Graph") <- uwot::umap(X = NULL, n_neighbors=100,n_components = 200, nn_method = nn)

 p1=scater:: plotReducedDim(sce2, dimred = "PCA", colour_by = "labels")+ggplot2::ggtitle(label = "UMAP_on_PCA")+scale_color_manual(values =newcolor )
#p2=scater:: plotReducedDim(sce2, dimred = "KNN",colour_by = "labels")+ ggplot2::ggtitle(label = "UMAP_on_ScaleData")
 p3=scater:: plotReducedDim(sce2,dimred = "UMAP_on_Graph", colour_by = "labels") + ggplot2::ggtitle(label = "UMAP_on_Graph")+scale_color_manual(values =newcolor )

 figure_list[[i]]=cowplot::plot_grid(p1,p3,nrow=1)

}
              

cowplot::plot_grid(plotlist = figure_list,nrow=3,labels=scdata_Samples_ID2$Sample_ID2,label_x = 0.35,label_y=1)
 
```

```{r,fig.height=16,fig.width=12}
Cell_anno=Mye_pred
Data=SF_data_Myeloid

for (i in 1:length(Data)){
 select_data=Cell_anno[[i]]
 select_scdata=Data[[i]]
 #all.markers <- metadata(select_data)$de.genes%>%.[unique(select_data)]
 #select_scdata$labels <-select_data$labels 
 Labels=intersect(unique(select_data),Main_celltype)%>%.[!grepl("Other",.)]

 empirical.markers <- scran::findMarkers(select_scdata,groups=select_data, direction="up")
 collected <- list()
 for (lab in Labels) {
  #  lab.markers <- unique(unlist(all.markers[[lab]]))
  #  m <- match(lab.markers, rownames(empirical.markers[[lab]]))
    m=rownames(empirical.markers[[lab]])[1:35]
  #  m <- lab.markers[rank(m) <= 25]
    collected[[lab]] <- scater::plotHeatmap(select_scdata, silent=TRUE,test.type="wilcox", order_columns_by="labels", main=lab, features=m)[[4]]
  }
 do.call(gridExtra::grid.arrange, collected)
# cowplot::plot_grid(plotlist =collected,ncol=3)
}
```


```{r,fig.height=18,fig.width=12,warning=F}
# Need scelist
scedata=scelist
plot_list=list()
for (i in 1:length(scedata)){
 sce3=scedata[[i]]
 newcolor=All_celltype_color
 plot_list[[i]]=scater::plotTSNE(sce3, colour_by="labels")+scale_color_manual(values =newcolor )
  

}

cowplot::plot_grid(plotlist = plot_list,nrow=5,labels=scdata_Samples_ID2$Sample_ID2)

```

```{r,fig.width=12,fig.height=10}
Mye_types=c("Macrophage",  "DC",  "Neutrophil", "Monocyte")
All_celltype_color=RColorBrewer::brewer.pal(n = 4, name = "Set1") 
names(All_celltype_color)=c(Mye_types)
```


```{r,fig.width=12,fig.height=10}
Data=SF_data_Myeloid
figure_list=list()
newcolor=All_celltype_color
 
for(i in 1:length(Data)){
set.seed(1234)
sce=Data[[i]]
sce$labels=gsub("s","",Mye_pred[[i]]$labels)
sce$labels=factor(sce$labels,levels = unique(Mye_pred[[i]]$labels))
dec <- modelGeneVarByPoisson(sce)
sce2 <- denoisePCA(sce, dec, subset.row=getTopHVGs(dec, n=5000))
nn <- RANN::nn2(reducedDim(sce2, "PCA"), k = 50)
names(nn) <- c("idx", "dist")
g <- buildKNNGraph(sce2, k = 30, use.dimred = "PCA")
reducedDim(sce2, "KNN") <- igraph::as_adjacency_matrix(g)


# Run UMAP and rename it for comparisson temp <- umap::umap.defaults
try(reducedDim(sce2, "UMAP_on_Graph") <- NULL)
reducedDim(sce2, "UMAP_on_Graph") <- uwot::umap(X = NULL, n_neighbors=100,n_components = 200, nn_method = nn)

p1=scater:: plotReducedDim(sce2, dimred = "PCA", colour_by = "labels")+ggplot2::ggtitle(label = "UMAP_on_PCA")+scale_color_manual(values =newcolor )
#p2=scater:: plotReducedDim(sce2, dimred = "KNN",colour_by = "labels")+ ggplot2::ggtitle(label = "UMAP_on_ScaleData")
p3=scater:: plotReducedDim(sce2,dimred = "UMAP_on_Graph", colour_by = "labels") + ggplot2::ggtitle(label = "UMAP_on_Graph")+scale_color_manual(values =newcolor )

figure_list[[i]]=cowplot::plot_grid(p1,p3,nrow=1)

}
              

cowplot::plot_grid(plotlist = figure_list,nrow=3,labels=scdata_Samples_ID2$Sample_ID2)
```

```{r,fig.width=12,fig.height=16}

pred.scData=Mye_pred[[1]]
Data=SF_data_Myeloid[[1]]
                     
for (i in 1:length(pred.scData)){
 select_data=pred.scData[[i]]
 select_scdata=Data[[i]]
 all.markers <- metadata(select_data)$de.genes%>%.[unique(select_data$labels)]
 #select_scdata$labels <-select_data$labels 
 Labels=intersect(unique(select_data$labels),Main_celltype)%>%.[!grepl("Other",.)]

 empirical.markers <- scran::findMarkers(select_scdata,groups=select_data$labels, direction="up")
 collected <- list()
 for (lab in Labels) {
    lab.markers <- unique(unlist(all.markers[[lab]]))
    m <- match(lab.markers, rownames(empirical.markers[[lab]]))
    m <- lab.markers[rank(m) <= 25]
    collected[[lab]] <- scater::plotHeatmap(select_scdata, silent=TRUE, order_columns_by="labels", main=lab, features=m)[[4]]
  }
 do.call(gridExtra::grid.arrange, collected)
# cowplot::plot_grid(plotlist =collected,ncol=3)
}


```

```{r}
knitr::knit_exit()
```


```{r,eval=F}

Mye_pred=list()
Select_Data=SF_data_Myeloid
  
for (i in 1:length(Select_Data)){
  scdata=Select_Data[[i]]
  Pred= SingleR::SingleR(test =scdata, ref = hpca.se, assay.type.test=1, labels =hpca.se$label.main,de.method="wilcox")
  table(pred.scData$labels)
  All_celltype=Pred$labels 
  #All_celltype_anno=data.frame(labels=All_celltype)%>%mutate(label2=ifelse(labels%in%Main_celltype,labels,"Other"))
  Pred$labels=All_celltype
  Mye_pred[[i]]=Pred
   
}
```


```{r,eval=T}
All_celltype_color=RColorBrewer::brewer.pal(n = 4, name = "Set1") 
names(All_celltype_color)=c(Mye_types) 

Main_celltype=c("B_cell","T_cells","NK_cell","Monocyte","Neutrophils","Macrophage","DC" ,"Platelets")

All_celltype_color=RColorBrewer::brewer.pal(n = 9, name = "Set1") 
names(All_celltype_color)=c(Main_celltype,"Other") 
```



# Inspired by http://bioconductor.org/books/release/SingleRBook/annotation-diagnostics.html#based-on-the-deltas-across-cells


```{r,eval=F}
scelist=list()
sc_data=SF_data_Myeloid
#Predict_data=Mye_pred
for (i in 1:length(sc_data)){
 set.seed(1234)
 sce=sc_data[[i]]
 #data=Clean_scdata[[i]]
 #sce <- logNormCounts(Seurat::as.SingleCellExperiment(data))
 dec <- modelGeneVarByPoisson(sce)
 sce2 <- denoisePCA(sce, dec, subset.row=getTopHVGs(dec, n=5000))
 colLabels(sce2) <- clusterRows(reducedDim(sce2), NNGraphParam())
 set.seed(117)
 scelist[[i]]<-scater::runTSNE(sce2, dimred="PCA")
#

}
```

```{r,include=F}
#save(scData2,pred.scData,scelist,file=file.path(Rawdata_path,"Pred_scdata.rdata"))
# load(file.path(Rawdata_path,"Pred_scdata.rdata")) # scData2: logscData with labels, Pred.data: singleR output, sce3
# 
# scdata_Samples_ID=lapply(scData2, function(x) as.character(x$orig.ident)%>%unique())%>%unlist()
# scdata_Samples_ID2=data.frame(SRR_number=scdata_Samples_ID)%>%left_join(.,SRA_sample_anno)

```

```{r,fig.height=18,fig.width=12,warning=F}
# Need scelist
All_celltype_color=RColorBrewer::brewer.pal(n = 4, name = "Set1") 
names(All_celltype_color)=c(Mye_types) 


plot_list=list()
for (i in 1:length(scelist)){
 sce3=scelist[[i]]
 newcolor=All_celltype_color[unique(sce3$labels)]
 plot_list[[i]]=scater::plotTSNE(sce3, colour_by="labels")+scale_color_manual(values =newcolor )
  

}

cowplot::plot_grid(plotlist = plot_list,nrow=5,labels=scdata_Samples_ID2$Sample_ID2)



```


```{r}
i=1
 sce=sc_data[[i]]

dec <- modelGeneVarByPoisson(sce)
sce2 <- denoisePCA(sce, dec, subset.row=getTopHVGs(dec, n=5000))
nn <- RANN::nn2(reducedDim(sce2, "PCA"), k = 30)
names(nn) <- c("idx", "dist")
g <- buildKNNGraph(sce2, k = 30, use.dimred = "PCA")
reducedDim(sce2, "KNN") <- igraph::as_adjacency_matrix(g)


# Run UMAP and rename it for comparisson temp <- umap::umap.defaults
try(reducedDim(sce2, "UMAP_on_Graph") <- NULL)
reducedDim(sce2, "UMAP_on_Graph") <- uwot::umap(X = NULL, n_components = 2, nn_method = nn)

```

```{r}
p1=scater:: plotReducedDim(sce2, dimred = "PCA", colour_by = "labels")+ggplot2::ggtitle(label = "UMAP_on_PCA")
p2=scater:: plotReducedDim(sce2, dimred = "KNN",colour_by = "labels")+ ggplot2::ggtitle(label = "UMAP_on_ScaleData")
p3=scater:: plotReducedDim(sce2,dimred = "UMAP_on_Graph", colour_by = "labels") + ggplot2::ggtitle(label = "UMAP_on_Graph")
```

```{r}
p3
```



```{r,fig.width=12,fig.height=16}
for (i in 1:length(pred.scData)){
 select_data=pred.scData[[i]]
 select_scdata=scData2[[i]]
 all.markers <- metadata(select_data)$de.genes%>%.[unique(select_data$labels)]
 #select_scdata$labels <-select_data$labels 
 Labels=intersect(unique(select_data$labels),Main_celltype)%>%.[!grepl("Other",.)]

 empirical.markers <- scran::findMarkers(select_scdata,groups=select_data$labels, direction="up")
 collected <- list()
 for (lab in Labels) {
    lab.markers <- unique(unlist(all.markers[[lab]]))
    m <- match(lab.markers, rownames(empirical.markers[[lab]]))
    m <- lab.markers[rank(m) <= 25]
    collected[[lab]] <- scater::plotHeatmap(select_scdata, silent=TRUE, order_columns_by="labels", main=lab, features=m)[[4]]
  }
 do.call(gridExtra::grid.arrange, collected)
# cowplot::plot_grid(plotlist =collected,ncol=3)
}


```

```{r}
knitr::knit_exit()
```


## check 
```{r}
i=12
select_data=pred.scData[[i]]
select_scdata=scData2[[i]]
to.remove2 <- pruneScores(select_data, min.diff.next=0)
table(Label=select_data$labels, Removed=to.remove2)
```


```{r}
all.markers <- metadata(select_data)$de.genes%>%.[unique(select_data$labels)]
names(all.markers)
T.markers <- unique(unlist(all.markers$T_cells))
select_scdata$labels <-select_data$labels

library(scater)
#BiocManager::install ("scater")
plotHeatmap(select_scdata, order_columns_by="labels", features=beta.markers)
```

```{r,fig.height=12,fig.width=10}
library(scran)
#BiocManager::install("scran")
empirical.markers <- findMarkers(select_scdata, select_scdata$labels, direction="up")
m <- match(T.markers, rownames(empirical.markers$beta))
m <- beta.markers[rank(m) <= 40]

library(scater)
plotHeatmap(select_scdata, order_columns_by="labels", features=m,scale=F)
```

```{r,fig.height=12,fig.width=12}
Main_celltypes=All_celltype_anno$labels[1:7]
 

for (i in 1:length(pred.scData)){

 select_data=pred.scData[[i]]
 select_scdata=scData2[[i]]
 all.markers <- metadata(select_data)$de.genes%>%.[unique(select_data$labels)]
 select_scdata$labels <-select_data$labels  
 empirical.markers <- findMarkers(select_scdata, select_scdata$labels, direction="up")
 collected <- list()
 #Labels=intersect(unique(select_data$labels),Main_celltypes)
 for (lab in Labels) {
    lab.markers <- unique(unlist(all.markers[[lab]]))
    m <- match(lab.markers, rownames(empirical.markers[[lab]]))
    m <- lab.markers[rank(m) <= 20]
    collected[[lab]] <- plotHeatmap(select_scdata, silent=TRUE, order_columns_by="labels", main=lab, features=m)[[4]]
  }
 do.call(gridExtra::grid.arrange, collected)
# cowplot::plot_grid(plotlist =collected,ncol=3)
}


```


```{r}
sce <- select_scdata
dec <- modelGeneVarByPoisson(sce)
sce2 <- denoisePCA(sce, dec, subset.row=getTopHVGs(dec, n=5000))
nn <- RANN::nn2(reducedDim(sce2, "PCA"), k = 30)
names(nn) <- c("idx", "dist")
g <- buildKNNGraph(sce2, k = 30, use.dimred = "PCA")
reducedDim(sce2, "KNN") <- igraph::as_adjacency_matrix(g)


# Run UMAP and rename it for comparisson temp <- umap::umap.defaults
try(reducedDim(sce2, "UMAP_on_Graph") <- NULL)
reducedDim(sce2, "UMAP_on_Graph") <- uwot::umap(X = NULL, n_components = 2, nn_method = nn)

```

```{r}
p1=plotReducedDim(sce2, dimred = "PCA", colour_by = "labels")+ggplot2::ggtitle(label = "UMAP_on_PCA")
p2= plotReducedDim(sce2, dimred = "KNN",colour_by = "labels")+ ggplot2::ggtitle(label = "UMAP_on_ScaleData")
p3= plotReducedDim(sce2,dimred = "UMAP_on_Graph", colour_by = "labels") + ggplot2::ggtitle(label = "UMAP_on_Graph")
```


```{r,fig.width=10,fig.height=6}
cowplot::plot_grid(ncol = 3, plotlist = list(p1,p2,p3))

```


```{r}
plotlist <- list()
for (i in c("CD3E", "CD4", "CD8A", "NKG7", "GNLY", "MS4A1", "CD14", "LYZ", "MS4A7",
    "FCGR3A", "CST3", "FCER1A")) {
    plotlist[[i]] <- plotReducedDim(sce2, dimred = "UMAP_on_PCA", colour_by = i, by_exprs_values = "logcounts") +
        scale_fill_gradientn(colours = colorRampPalette(c("grey90", "orange3", "firebrick",
            "firebrick", "red", "red"))(10)) + ggtitle(label = i) + theme(plot.title = element_text(size = 20))
}
plot_grid(ncol = 3, plotlist = plotlist)
```


```{r}
knitr::knit_exit()
```


```{r}
#library(patchwork)

Raw_scdata=list()
ggfigure=list()
for ( i in SRA_sample_anno$SRR_number ) {
 case1=i
 SC_out=file.path(SRR_path,case1,"run_count","outs","filtered_feature_bc_matrix" )
 pbmc.data=Read10X(data.dir = SC_out)

 pbmc <- CreateSeuratObject(counts = pbmc.data, project = case1, min.cells = 3, min.features = 200)
 pbmc[["percent.mt"]] <- PercentageFeatureSet(pbmc, pattern = "^MT-")
 Raw_scdata[[i]]=pbmc
# Visualize QC metrics as a violin plot
 ggfigure[[i]]=VlnPlot(pbmc, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
 
}
 
```


```{r,fig.width=16,fig.height=32,eval=F}
Out=cowplot::plot_grid(ggfigure,nrow=length(ggfigure),labels = names(ggfigure) )
ggfigure[[2]]
p2=ggfigure[[2]]
p3=ggfigure[[3]]
library(ggplot2)
library(gtable)
g2 <- ggplotGrob(p2)
g3 <- ggplotGrob(p3)
g <- rbind(g2, g3, size = "first")
g$widths <- grid::unit.pmax(g2$widths, g3$widths)
grid::grid.newpage()
grid::grid.draw()

 
```


```{r,fig.width=16,fig.height=32,include=T}
cowplot::plot_grid(ggfigure[[1]],ggfigure[[2]],ggfigure[[3]],ggfigure[[4]],ggfigure[[5]],ggfigure[[6]],ggfigure[[7]],ggfigure[[8]],ggfigure[[9]],ggfigure[[10]], ggfigure[[11]],ggfigure[[12]],ggfigure[[13]],ggfigure[[14]],ggfigure[[15]],ncol=3,nrow=5,labels = names(ggfigure),label_y = 1.01)

```

```{r}
Metadata=list()
for ( i in names(Raw_scdata) ) {
   Data=Raw_scdata[[i]]
   Metadata[[i]]=data.frame(nGene=Data[["nCount_RNA"]],nUMI=Data[["nFeature_RNA"]],Percent_MT=Data[["percent.mt"]])%>%setNames(c("nGene","nUMI","percent.mito"))
}

Metadata[[1]]
names(Metadata)
```
# filter cells (https://matthieuxmoreau.github.io/EarlyPallialNeurogenesis/html-Reports/Quality_Control.html)

```{r}
Clean_cell_list=list()
plot_list=list()
for (i in names(Metadata) ){
 
   # Set low and high thresholds Mito percentage
  Cell.QC.Stat=Metadata[[i]]
  
  max.mito.thr <- median(Cell.QC.Stat$percent.mito) + 3*mad(Cell.QC.Stat$percent.mito)
  min.mito.thr <- median(Cell.QC.Stat$percent.mito) - 3*mad(Cell.QC.Stat$percent.mito)
  p1 <- ggplot(Cell.QC.Stat, aes(x=nGene, y=percent.mito)) +
      geom_point() +geom_hline(aes(yintercept = max.mito.thr), colour = "red", linetype = 2) +
      geom_hline(aes(yintercept = min.mito.thr), colour = "red", linetype = 2) +
      annotate(geom = "text",size=2 ,label = paste0(as.numeric(table(Cell.QC.Stat$percent.mito > max.mito.thr | Cell.QC.Stat$percent.mito < min.mito.thr)[2])," cells removed\n", as.numeric(table(Cell.QC.Stat$percent.mito > max.mito.thr | Cell.QC.Stat$percent.mito < min.mito.thr)[1])," cells remain"), x = max(Cell.QC.Stat$nGene)/2, y = max(Cell.QC.Stat$percent.mito)/2)
p1=ggExtra::ggMarginal(p1, type = "histogram", fill="lightgrey", bins=100)   
p1
Cell.QC.Stat2 <- Cell.QC.Stat %>% filter(percent.mito < max.mito.thr) %>% filter(percent.mito > min.mito.thr)
 
# Set high threshold on the number of transcripts
max.nUMI.thr <- median(log10(Cell.QC.Stat2$nUMI)) + 3*mad(log10(Cell.QC.Stat$nUMI))
min.Genes.thr <- median(log10(Cell.QC.Stat2$nGene)) - 3*mad(log10(Cell.QC.Stat2$nGene))
max.Genes.thr <- median(log10(Cell.QC.Stat2$nGene)) + 3*mad(log10(Cell.QC.Stat2$nGene))

 # Gene/UMI scatter plot before filtering
p2 <- ggplot(Cell.QC.Stat2, aes(x=log10(nUMI), y=log10(nGene))) +
      geom_point() +
      geom_smooth(method="lm") +
      geom_hline(aes(yintercept = min.Genes.thr), colour = "green", linetype = 2) +
      geom_hline(aes(yintercept = max.Genes.thr), colour = "green", linetype = 2) +
      geom_vline(aes(xintercept = max.nUMI.thr), colour = "red", linetype = 2)

p2=ggExtra::ggMarginal(p2, type = "histogram", fill="lightgrey")
  
  # Set low and hight thresholds on the number of detected genes




# filtered by nGene and uUMI
Cell.QC.Stat3 <- Cell.QC.Stat2 %>% filter(log10(nGene) > min.Genes.thr) %>% filter(log10(nUMI) < max.nUMI.thr)
lm.model <- lm(data = Cell.QC.Stat2, formula = log10(nGene) ~ log10(nUMI))
p3 <- ggplot(Cell.QC.Stat3, aes(x=log10(nUMI), y=log10(nGene))) +
  geom_point() +
  geom_smooth(method="lm") +
  geom_hline(aes(yintercept = min.Genes.thr), colour = "green", linetype = 2) +
  geom_hline(aes(yintercept = max.Genes.thr), colour = "green", linetype = 2) +
  geom_vline(aes(xintercept = max.nUMI.thr), colour = "red", linetype = 2) +
  geom_abline(intercept =lm.model$coefficients[1] - 0.2 , slope = lm.model$coefficients[2], color="orange") +
  annotate(geom = "text", size=2,label = paste0(dim(Cell.QC.Stat3)[1], " QC passed cells"), x =3.5, y = 4.5)

p3=ggExtra::ggMarginal(p3, type = "histogram", fill="lightgrey")
#  Cells to exclude lie below an intersept offset of -0.18
Cell.QC.Stat3$valideCells <- log10(Cell.QC.Stat3$nGene) > (log10(Cell.QC.Stat3$nUMI) * lm.model$coefficients[2] + 
                                                           (lm.model$coefficients[1] - 0.2))

p4 <- ggplot(Cell.QC.Stat3, aes(x=log10(nUMI), y=log10(nGene))) +
  geom_point(aes(colour = valideCells)) +
  geom_smooth(method="lm") +
  geom_abline(intercept = lm.model$coefficients[1] - 0.2 , slope = lm.model$coefficients[2], color="orange") + 
  theme(legend.position="none") +
  annotate(geom = "text",size=2, label = paste0(as.numeric(table(Cell.QC.Stat$valideCells)[2]), " QC passed cells\n",
                                         as.numeric(table(Cell.QC.Stat$valideCells)[1]), " QC filtered"), x = 4, y = 3.8)

p4 
# Remove unvalid cells
Cell.QC.Stat4 <- Cell.QC.Stat3 %>% filter(valideCells)  
 
Clean_cell_list[[i]]=Cell.QC.Stat4

plot_row=cowplot::plot_grid(p1,p2,p3,p4,nrow=1)
title <- cowplot::ggdraw() + 
  cowplot::draw_label(i,
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
out=cowplot::plot_grid(
  title, plot_row,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
 plot_list[[i]]=out
}

 
 
```
# Plot filter process
```{r,fig.width=18,fig.height=24,include=T}
library(gridExtra)
do.call("grid.arrange", c(plot_list, ncol=2,nrow=8))
```

```{r}
Clean_scdata=list()
for (i in 1:length(Raw_scdata)){
Clean_data=Clean_cell_list[[i]]

Clean_ID=Clean_data%>%mutate(State="Good",ID=rownames(.))
scData=Raw_scdata[[i]]
scData[["CellName"]]=colnames(scData)
Clean_scdata[[i]]= subset(scData , subset = CellName %in% rownames(Clean_data))

}

```
```{r}
#save(SRA_sample_anno,Clean_scdata,file=file.path(Rawdata_path,"Clean_scRNA_and_metadata.rdata")
 
```


```{r}
knitr::knit_exit()
```

```{r,fig.width=10}
plot1 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
plot1 + plot2
```
```{r}
save(SRA_sample_anno,clean)

```

```{r}
pbmc_norm <- NormalizeData(pbmc_subset, normalization.method = "LogNormalize", scale.factor = 10000)
```

